Approximate Code: A Cost-Effective Erasure Code for Video Applications in Cloud Storage Systems

### 2019-03-30 ApproximateCode.tex
version 0.4.5

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

@@

\begin{table*}[ht]
\centering
\caption{Summary on Various Erasure Codes}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Name & Fault Tolerance & Storage Overhead & Scalibility & Recovery Cost & \begin{tabular}[c]{@{}c@{}}Computational\\ Complexity\end{tabular} \\ \hline \hline
RS($k,m$) Code & any $m$ disks & $m$ disks & high & high & high \\ \hline
MSR($k,m$) Code & any $m$ disks & $m$ disks & medium & low & very high \\ \hline
Raid 6 & 2 & 2 & low & high & low \\ \hline
SD Code($m,s$) & any $m$ disks and $s$ sectors & $m$ disks and $s$ sectors & low & low & medium \\ \hline
\begin{tabular}[c]{@{}c@{}}Approximate Code($n,m,s,t$)\\ (Important Data)\end{tabular} & any $m+s$ disks & $m$ disks and $s$ sectors & high & high & medium \\ \hline
\begin{tabular}[c]{@{}c@{}}Approximate Code($n,m,s,t$)\\ (Ordinary Data)\end{tabular} & any $m$ disks & $m$ disks and $s$ sectors & high & high & high \\ \hline
\end{tabular}
\end{table*}

@@

\subsection{Video Frame Recovery: Frame Interpolation}
In the circumstance of data loss, it's common to lose some frames and then the video is not complete. One easy way to solve this problem is to store consecutive frames in different disks, so the video is still good for displaying only with fewer frame rates. Another alternative is that we can actually recover the lost frames by applying the a technique named video frame interpolation.

@@

All the frame interpolation method are based on that we have the input of full images of two consecutive frames (maybe one or two missing in the middle). However, in the popular coding format like H.264, only I frame have full image data of itself, and all the other image data is dependent on that in I frames. Without an I frame, the following ones that depend on it will go invalid and be impossible for recovery which means I frames require more storage overhead to ensure its integrity and reliability.

@@

Based on the above definition, our design has 4 configurable parameters $(n, m, s,t)$ that uniquely determine the construction of Approximate Code.
Figure \ref{apcode-7222-v5} shows an example of Approximate Codes with $n = 7$, $m = 2$, $s=2$ and $t = 2$, where we label the data disks with $d_{i,j}$, the important data parity sectors with $q_{i,j}$ and the normal parity sectors with $p_{i,j}$.

\begin{figure}[htbp]
\centering
\includegraphics[width=0.45\textwidth]{photo/apcode-7222-v5.PDF}
\caption{A sample of Approximate Codes $(7,2,2,2)$ with 7 chunks where 2 of them are parity chunks (orange blocks) and 4 other sectors (red blocks) are designed for encoding important data. In this example, there are 6 sectors (dark blue blocks) for important data and 15 sectors (light blue blocks) for normal data.}
\label{apcode-7222-v5}
\end{figure}

@@

In general, Approximate Code performs extra parities on important data.
Since our design guarantees the important data, the important parity and the normal data blocks completely fill $n-m$ chunks, we can construct the remaining $m$ parity chunks in any way, as long as their parity method are linearly independent of the way the important parity blocks are. Therefore, EC methods such as RS-based codes, XOR-based codes or MSR codes can be used to construct Approximate Code because it is essentially a way of data classification and data distribution, and current EC schemes do not assume anything about data feature.

\subsection{Encoding and Decoding Process}

The encoding process can be divided into two phases: the important coding phase (\emph{I-Phase}) and the global coding phase (\emph{G-Phase}). . .

In \emph{I-Phase}, $s$ groups of important parity sectors are generated

The decoding process can be divided into two modes: the approximate recovery mode (A-model) and the full recovery mode (F-model). . .

\textcolor{blue}{We introduce RS-based and XOR-based Approximate Code due to space limitations}
\subsubsection{RS-based Approximate Code}

In \emph{phase 1}, we use RS$(h,s)$ to encode $h$ groups of important data sectors and generate $s$ groups of parity sectors labeled with $q_{i,j}$. The calculation of $q_{i,j}$ are defined by equation \ref{q_ij}, where $\alpha_k$ is the coefficient in Galois Field (GF). 
For example, $q_{1,1} = \alpha_0 d_{1,0} + \alpha_1 d_{1,1} + \alpha_2 d_{1,2}$.
As shown in the blod box in Figure \ref{apcode-7222-v5}, we use RS(3,2) in this phase.
\begin{equation}\label{q_ij}
    q_{i,j} = \sum_{k=0}^{h-1} \alpha_k^{j} d_{i,k}
\end{equation}

In \emph{phase 2}, we use RS$(n-m,m)$ to generate $m$ parity chunks labeled with $p_{i,j}$ from $n-m$ chunks consist of data sectors and important parity sectors. The calculation of $p_{i,j}$ are defined by equation \ref{p_ij_1} and \ref{p_ij_2}.
Despite the difference in expression, the encoding process for $p_{i,j(i<t)}$ and $p_{i,j(i \geqslant t)}$ are same on chunk level because we treat $q_{i,j}$ and $b_{i,j}$ as the same on chunk level.
For example, $p_{1,1} = \alpha_0^3 d_{1,0} + \alpha_1^3 d_{1,1} + \alpha_2^3 d_{1,2} + \alpha_3^3 q_{1,0} + \alpha_4^3 q_{1,1}$.
As shown in orange chunks in Figure \ref{apcode-7222-v5}, we use RS(5,2) in this phase.

\begin{equation}\label{p_ij_1}
    \mathop{p_{i,j}}\limits_{i<t} = 
    \sum_{k=0}^{h-1} \alpha_k^{s+j} d_{i,k} +
    \sum_{l=0}^{s-1} \alpha_{l+h}^{s+j} q_{i,l}
\end{equation}
\begin{equation}\label{p_ij_2}
    \mathop{p_{i,j}}\limits_{i \geqslant t} = 
    \sum_{k=0}^{n-m-1} \alpha_k^{s+j} d_{i,k}
\end{equation}

\subsubsection{Decoding Process}
The decoding process can be partitioned into two modes: full recovery mode and approximate recovery mode. When no more than $m$ chunks lost, the system can fully recover.

\subsection{Proof of Correctness}
\subsection{Data Distribution}\label{Data Distribution}
\subsection{Properties of Approximate Code}

@@

%
% The next two lines define the bibliography style to be used, and the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{ApproximareCode}

>>>>

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\usepackage{subfigure}

@@

\begin{table*}[ht]
\centering
\caption{Summary on Various Erasure Codes}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Name & Fault Tolerance & Storage Overhead & Scalibility & Recovery Cost & \begin{tabular}[c]{@{}c@{}}Computational\\ Complexity\end{tabular} \\ \hline \hline
RS($k,m$) Code & any $m$ disks & $m$ disks & high & high & high \\ \hline
MSR($k,m$) Code & any $m$ disks & $m$ disks & medium & low & very high \\ \hline
Raid 6 & 2 & 2 & low & high & low \\ \hline
SD Code($m,s$) & any $m$ disks and $s$ sectors & $m$ disks and $s$ sectors & low & low & medium \\ \hline
\begin{tabular}[c]{@{}c@{}}Approximate Code($n,m,s,t$)\\ (Important Data)\end{tabular} & any $m+s$ disks & $m$ disks and $s$ sectors & high & high & medium \\ \hline
\begin{tabular}[c]{@{}c@{}}Approximate Code($n,m,s,t$)\\ (Minor Data)\end{tabular} & any $m$ disks & $m$ disks and $s$ sectors & high & high & high \\ \hline
\end{tabular}
\end{table*}

@@

\textcolor{red}{We define I frames are our important data}

\subsection{Video Frame Recovery: Frame Interpolation}
\textcolor{red}{Add something related to the former subsection}

\textcolor{blue}{In the circumstance of video approximate storage, it's common to lose some minor data making the video incomplete...}

In the circumstance of data loss, it's common to lose some frames and then the video is not complete. One easy way to solve this problem is to store consecutive frames in different disks, so the video is still good for displaying only with fewer frame rates. Another alternative is that we can actually recover the lost frames by applying the a technique named video frame interpolation.

@@

\textcolor{blue}{All the frame interpolation method are based on that we have the input of full images of two consecutive frames (maybe one or two missing in the middle). However, in the popular coding format like H.264, only I frame have full image data of itself, and all the other image data is dependent on that in I frames. Without an I frame, the following ones that depend on it will go invalid and be impossible for recovery which means I frames require more storage overhead to ensure its integrity and reliability.}

@@

Based on the above definition, our design has 4 configurable parameters $(n, m, s,t)$ that uniquely determine the construction of Approximate Code.
Figure \ref{apcode-7222-v5} shows an example of Approximate Codes with $n = 7$, $m = 2$, $s=2$ and $t = 2$, where we label the data disks with $d_{i,j}$, the important data parity sectors with $q_{i,j}$ and the minor parity sectors with $p_{i,j}$.

We then define the set of sectors as follows:
\begin{itemize}
    \item Important data sector set $D_I=\{d_{i,j}|0\leqslant i < t, 0\leqslant j < h \}$
    \item Minor data sector set $D_M=\{d_{i,j}|0\leqslant i < t, 0\leqslant j < n-m \}$
    \item Important parity sector set $Q=\{q_{i,j}|0\leqslant i < t, 0\leqslant j < s \}$
    \item Global parity sector set $G=\{p_{i,j}|0\leqslant i < r, 0\leqslant j < m \}$
\end{itemize}

\begin{figure}[h]
\centering

\subfigure[sector label and encoding process]{
    \includegraphics[width=0.32\textwidth]{photo/apcode-7222-v5.PDF}
    \label{apcode-7222-v5-a}
}
\subfigure[sector sets]{
    \includegraphics[width=0.13\textwidth]{photo/DDQG.PDF}
    \label{apcode-7222-v5-b}
}
\caption{A sample of Approximate Codes $(7,2,2,2)$ with 7 chunks where 2 of them are parity chunks (orange set $G$) and 4 other sectors (red set $Q$) are designed for encoding important data. In this example, there are 6 sectors (dark blue set $D_I$) for important data and 15 sectors (light blue set $D_M$) for minor data.}
\label{apcode-7222-v5}
\end{figure}

@@

In general, Approximate Code performs extra parities on important data.
Since our design guarantees the important data, the important parity and the minor data blocks completely fill $n-m$ chunks, we can construct the remaining $m$ parity chunks in any way, as long as their parity method are linearly independent of the way the important parity blocks are. Therefore, EC methods such as RS-based codes, XOR-based codes or MSR codes can be used to construct Approximate Code because it is essentially a way of data classification and data distribution, and current EC schemes do not assume anything about data feature.

\subsection{Encoding and Decoding Process}
In this section, we use Figure \ref{apcode-7222-v5} to illustrate the encoding and decoding process of Approximate Code(7,2,2,2).

The encoding process consists of two phases: the important coding phase (\emph{I-Phase}) and the global coding phase (\emph{G-Phase}). 
The \emph{I-Phase} is expressed as two red arrows in the blod box, where $Q$ is generated to verify $D_I$, and
the \emph{G-Phase} is expressed as a yellow triangle arrow, where $G$ is generated to verify $D_I$, $D_M$ and $Q$.

The decoding process provides two modes: the approximate recovery mode and the full recovery mode.
When no more than $m$ divices fail, Approximate Code guarantees full recovery of lost data.
It should be noted that in the calculation of $G$ in \emph{G-Phase} and in the decoding process in full recovery mode, we consider $D_I$, $D_M$ and $Q$ as the same, so the minimum coding unit is chunk. When the number of failed devices is larger than $m$ but no more than $m+s$, Approximate Code guarantees full recovery of lost important data, which require $D_I$, $Q$ and part of $G$ for joint recovery.

\textcolor{blue}{We then introduce RS-based and XOR-based Approximate Code}
\subsubsection{RS-based Approximate Code}

In \emph{I-Phase}, we use RS(3,2) to encode 3 groups of important data sectors and generate 2 groups of parity sectors labeled with $q_{i,j}$. The calculation of $q_{i,j}$ are defined by equation \ref{q_ij}, where $\alpha_k$ is the coefficient in Galois Field (GF). The coding coefficient matrix is transformed from the Vandermonde matrix by elementary transformation.
\textcolor{blue}{Coding matrix?}

\iffalse
\begin{equation}
\begin{pmatrix} 
1&  1&  1\\
\alpha_0 & \alpha_1 & \alpha_2 \\
\alpha_0^2+\alpha_3^2+\alpha_4^2*\alpha_0 & \alpha_1^2 +\alpha_3^2+\alpha_4^2*\alpha_1 & \alpha_2^2+\alpha_3^2+\alpha_4^2*\alpha_2  \\
\alpha_0^3+\alpha_3^3+\alpha_4^3*\alpha_0 & \alpha_1^3 +\alpha_3^3+\alpha_4^3*\alpha_1 & \alpha_2^3+\alpha_3^3+\alpha_4^3*\alpha_2  \\
\end{pmatrix} 
\end{equation}
\fi

For example, $q_{1,1} = \alpha_0 d_{1,0} + \alpha_1 d_{1,1} + \alpha_2 d_{1,2}$.
\begin{equation}\label{q_ij}
    q_{i,j} = \sum_{k=0}^{h-1} \alpha_k^{j} d_{i,k}
\end{equation}

In \emph{I-Phase}, we use RS(5,2) to generate 2 parity chunks labeled with $p_{i,j}$ from 5 chunks consist of data sectors and important parity sectors. The calculation of $p_{i,j}$ are defined by equation \ref{p_ij_1} and \ref{p_ij_2}.
For example, $p_{1,1} = \alpha_0^3 d_{1,0} + \alpha_1^3 d_{1,1} + \alpha_2^3 d_{1,2} + \alpha_3^3 q_{1,0} + \alpha_4^3 q_{1,1}$.

\begin{equation}\label{p_ij_1}
    \mathop{p_{i,j}}\limits_{i<t} = 
    \sum_{k=0}^{h-1} \alpha_k^{s+j} d_{i,k} +
    \sum_{k=0}^{s-1} \alpha_{k+h}^{s+j} q_{i,k}
\end{equation}
\begin{equation}\label{p_ij_2}
    \mathop{p_{i,j}}\limits_{i \geqslant t} = 
    \sum_{k=0}^{n-m-1} \alpha_k^{s+j} d_{i,k}
\end{equation}

The full recovery decoding process of RS-based Approximate Code is obvious since it is the same as the decoding process of RS(5,2).
For the approximate decoding process, there are 4 independent equations that can tolerate any 4 disk failures because the coding coefficient matrix is full rank.

\subsection{Proof of Correctness}
\subsection{Data Distribution}\label{Data Distribution}

\subsection{Properties of Approximate Code}

@@

%
% The next two lines define the bibliography style to be used, and the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{ApproximateCode}
